\pkg{casebase}: An Alternative Framework For Survival Analysis

### 2020-07-20 analysis/paper/paper.Rmd

```{r plot-stratified-erspc-data, eval = eval_cs1, echo = FALSE, fig.width=7, fig.height=5, fig.asp=0.75, fig.cap="Population time plot for ERSPC data."}
plot(pt_object, 
     add.base.series = TRUE,
     ratio = 0.7,
     facet.params = list(ncol = 2),
     ribbon.params = list(fill = "gray50"),
     case.params = list(size = 0.8),
     base.params = list(size = 0.8)) + 
  paper_gg_theme +  
  scale_y_continuous(labels = label_number_si())
```

>>>>

```{r plot-stratified-erspc-data, eval = eval_cs1, echo = FALSE, fig.width=7, fig.height=5, fig.asp=0.75, fig.cap="Population time plot for ERSPC data."}

label_number_si <- function (accuracy = 1, unit = NULL, sep = NULL, ...) {
    sep <- if (is.null(unit)) 
        ""
    else " "
    scales:::force_all(accuracy, ...)
    function(x) {
        breaks <- c(0, 10^c(K = 3, M = 6, B = 9, T = 12))
        n_suffix <- cut(abs(x), breaks = c(unname(breaks), Inf), 
            labels = c(names(breaks)), right = FALSE)
        n_suffix[is.na(n_suffix)] <- ""
        suffix <- paste0(sep, n_suffix, unit)
        scale <- 1/breaks[n_suffix]
        scale[which(scale %in% c(Inf, NA))] <- 1
        number(x, accuracy = accuracy, scale = unname(scale), 
            suffix = suffix, ...)
    }
}
plot(pt_object, 
     add.base.series = TRUE,
     ratio = 0.7,
     facet.params = list(ncol = 2),
     ribbon.params = list(fill = "gray50"),
     case.params = list(size = 0.8),
     base.params = list(size = 0.8)) + 
  paper_gg_theme +  
  scale_y_continuous(labels = label_number_si())
```

### 2020-07-20 analysis/paper/paper.tex

\begin{CodeInput}
R> # Compute hazards---
R> # First, create a list of time points for both exposure status
R> hazard_data <- expand.grid(
R>   exposure = c(0, 1),
R>   futime = seq(0, 1000,
R>     length.out = 100
R>   )
R> )
R> 
R> # Set the offset to zero
R> hazard_data$offset <- 0
R> # Use predict to get the fitted values, and exponentiate to
R> # transform to the right scale
R> hazard_data$hazard <- exp(predict(fit4,
R>   newdata = hazard_data,
R>   type = "link"
R> ))
R> # Add labels for plots
R> hazard_data$Status <- factor(hazard_data$exposure,
R>   labels = c("NoTrans", "Trans")
R> )
R> 
R> ggplot(hazard_data, aes(futime, hazard, colour = Status)) +
R>   geom_line() +
R>   theme_minimal() +
R>   theme(legend.position = "top") +
R>   ylab("Hazard") +
R>   xlab("Follow-up time")
\end{CodeInput}
\end{CodeChunk}

@@

This report was generated on 2020-07-18 15:04:50 using the following
computational environment and dependencies:

>>>>

\begin{CodeInput}
R> # Compute hazards---
R> # First, create a list of time points for both exposure status
R> hazard_data <- expand.grid(
R>   exposure = c(0, 1),
R>   futime = seq(0, 1000,
R>     length.out = 100
R>   )
R> )
R> 
R> # Set the offset to zero
R> hazard_data$offset <- 0
R> # Use predict to get the fitted values, and exponentiate to
R> # transform to the right scale
R> hazard_data$hazard <- exp(predict(fit4,
R>   newdata = hazard_data,
R>   type = "link"
R> ))
R> # Add labels for plots
R> hazard_data$Status <- factor(hazard_data$exposure,
R>   labels = c("NoTrans", "Trans")
R> )
R> 
R> ggplot(hazard_data, aes(futime, hazard, colour = Status)) +
R>   geom_line() +
R>   paper_gg_theme +  
R>   ylab("Hazard") +
R>   xlab("Follow-up time")
\end{CodeInput}
\end{CodeChunk}

@@

This report was generated on 2020-07-19 18:02:45 using the following
computational environment and dependencies:
